TEMPERATURES AND METALLICITIES OF M DWARFS IN THE APOGEE SURVEY

### 2019-08-01 paper/draft.tex
fix table length issue

\begin{deluxetable}{ccccc}
\tablecaption{Strong $\teff$-correlated molecular lines for all features with significance greater than $2\sigma_{\rm jackknife}$. `Significance' quantifies the number of standard deviations that the derivative of the line is significant to (with negative corresponding to negative derivatives).}
\tablehead{\colhead{Species} & \colhead{Wavelength} & \colhead{Derivative} & \colhead{$\sigma_{\rm jackknife}$} & \colhead{Significance}}
	\startdata
	FeH & 16107.127 & -0.002 & 0.001 & -2.78 \\
	FeH & 16245.463 & -0.005 & 0.002 & -3.214 \\
	FeH & 16271.519 & -0.002 & 0.001 & -2.013 \\
	FeH & 16284.562 & -0.006 & 0.001 & -5.807 \\
	FeH & 16377.066 & -0.005 & 0.001 & -4.554 \\
	FeH & 16741.489 & -0.002 & 0.001 & -2.873 \\
	FeH & 16812.415 & -0.004 & 0.001 & -4.241 \\
	FeH & 16813.808 & -0.006 & 0.001 & -3.954 \\
	FeH & 16922.405 & -0.003 & 0.001 & -3.867 \\
	FeH & 16934.801 & -0.004 & 0.001 & -3.591 \\
	OH & 15278.267 & 0.006 & 0.003 & 2.47 \\
	OH & 15280.8 & 0.004 & 0.002 & 2.007 \\
	OH & 15391.186 & 0.006 & 0.003 & 2.127 \\
	OH & 15407.355 & 0.01 & 0.002 & 4.836 \\
	OH & 15409.271 & 0.008 & 0.002 & 4.683 \\
	OH & 15505.797 & 0.009 & 0.003 & 3.511 \\
	OH & 15560.305 & 0.008 & 0.002 & 3.865 \\
	OH & 15565.895 & 0.005 & 0.002 & 2.505 \\
	OH & 15568.691 & 0.007 & 0.001 & 4.929 \\
	OH & 15572.133 & 0.008 & 0.002 & 4.393 \\
	OH & 16052.7 & 0.008 & 0.002 & 3.517 \\
	OH & 16055.362 & 0.006 & 0.002 & 3.7 \\
	OH & 16061.796 & 0.007 & 0.003 & 2.502 \\
	OH & 16065.124 & 0.009 & 0.002 & 4.214 \\
	OH & 16069.564 & 0.008 & 0.003 & 3.275 \\
	OH & 16074.227 & 0.007 & 0.002 & 3.338 \\
	OH & 16190.345 & 0.007 & 0.003 & 2.498 \\
	OH & 16192.134 & 0.008 & 0.002 & 4.012 \\
	OH & 16203.995 & 0.006 & 0.002 & 3.039 \\
	OH & 16207.129 & 0.004 & 0.002 & 2.196 \\
	OH & 16352.196 & 0.007 & 0.002 & 3.609 \\
	OH & 16354.682 & 0.011 & 0.003 & 4.167 \\
	OH & 16364.626 & 0.007 & 0.003 & 2.661 \\
	OH & 16368.244 & 0.008 & 0.002 & 4.303 \\
	OH & 16581.281 & 0.008 & 0.002 & 4.41 \\
	OH & 16581.74 & 0.004 & 0.001 & 4.842 \\
	OH & 16866.621 & 0.005 & 0.001 & 3.169 \\
	OH & 16871.982 & 0.012 & 0.002 & 4.892 \\
	OH & 16878.976 & 0.006 & 0.002 & 3.807 \\
	OH & 16884.573 & 0.005 & 0.002 & 3.066 \\
	OH & 16886.206 & 0.006 & 0.001 & 5.131 \\
	OH & 16895.074 & 0.005 & 0.002 & 2.197 \\
	\nodata & \nodata & \nodata & \nodata & \nodata
	\enddata
\end{deluxetable} \label{table:teff_derivative}

\begin{deluxetable}{ccccc}
\tablecaption{Strong $\teff$-correlated atomic lines for all features with significance greater than $2\sigma_{\rm jackknife}$.}
\tablehead{\colhead{Species} & \colhead{Wavelength} & \colhead{Derivative} & \colhead{$\sigma_{\rm jackknife}$} & \colhead{Significance}}
	\startdata
	\nodata & \nodata & \nodata & \nodata & \nodata \\
	Fe I & 15207.509 & -0.007 & 0.003 & -2.622 \\
	Fe I & 15648.478 & -0.006 & 0.002 & -3.273 \\
	Fe I & 15692.643 & -0.008 & 0.002 & -4.056 \\
	Si I & 15960.044 & -0.009 & 0.004 & -2.523 \\
	Si I & 16094.893 & -0.014 & 0.003 & -4.368 \\
	Si I & 16680.77 & -0.01 & 0.003 & -3.475 \\
	K I & 15162.824 & -0.006 & 0.002 & -2.294 \\
	Ti I & 15715.641 & 0.006 & 0.002 & 2.894 \\
	Ti I & 16634.973 & 0.003 & 0.001 & 4.224 \\
	V I & 15923.924 & 0.003 & 0.001 & 3.6 \\
	Mn I & 15159.054 & -0.006 & 0.002 & -3.123 \\
	\enddata
\end{deluxetable}

>>>>

\startlongtable
\begin{deluxetable}{ccccc}
\tablecaption{Strong $\teff$-correlated atomic and molecular lines for all features with significance greater than $2\sigma_{\rm jackknife}$. `Significance' quantifies the number of standard deviations that the derivative of the line is significant to (with negative corresponding to negative derivatives).}
\label{table:teff_derivative}
\tablehead{\colhead{Species} & \colhead{Wavelength} & \colhead{Derivative} & \colhead{$\sigma_{\rm jackknife}$} & \colhead{Significance}}
	\startdata
	FeH & 16107.127 & -0.002 & 0.001 & -2.78 \\
	FeH & 16245.463 & -0.005 & 0.002 & -3.214 \\
	FeH & 16271.519 & -0.002 & 0.001 & -2.013 \\
	FeH & 16284.562 & -0.006 & 0.001 & -5.807 \\
	FeH & 16377.066 & -0.005 & 0.001 & -4.554 \\
	FeH & 16741.489 & -0.002 & 0.001 & -2.873 \\
	FeH & 16812.415 & -0.004 & 0.001 & -4.241 \\
	FeH & 16813.808 & -0.006 & 0.001 & -3.954 \\
	FeH & 16922.405 & -0.003 & 0.001 & -3.867 \\
	FeH & 16934.801 & -0.004 & 0.001 & -3.591 \\
	OH & 15278.267 & 0.006 & 0.003 & 2.47 \\
	OH & 15280.8 & 0.004 & 0.002 & 2.007 \\
	OH & 15391.186 & 0.006 & 0.003 & 2.127 \\
	OH & 15407.355 & 0.01 & 0.002 & 4.836 \\
	OH & 15409.271 & 0.008 & 0.002 & 4.683 \\
	OH & 15505.797 & 0.009 & 0.003 & 3.511 \\
	OH & 15560.305 & 0.008 & 0.002 & 3.865 \\
	OH & 15565.895 & 0.005 & 0.002 & 2.505 \\
	OH & 15568.691 & 0.007 & 0.001 & 4.929 \\
	OH & 15572.133 & 0.008 & 0.002 & 4.393 \\
	OH & 16052.7 & 0.008 & 0.002 & 3.517 \\
	OH & 16055.362 & 0.006 & 0.002 & 3.7 \\
	OH & 16061.796 & 0.007 & 0.003 & 2.502 \\
	OH & 16065.124 & 0.009 & 0.002 & 4.214 \\
	OH & 16069.564 & 0.008 & 0.003 & 3.275 \\
	OH & 16074.227 & 0.007 & 0.002 & 3.338 \\
	OH & 16190.345 & 0.007 & 0.003 & 2.498 \\
	OH & 16192.134 & 0.008 & 0.002 & 4.012 \\
	OH & 16203.995 & 0.006 & 0.002 & 3.039 \\
	OH & 16207.129 & 0.004 & 0.002 & 2.196 \\
	OH & 16352.196 & 0.007 & 0.002 & 3.609 \\
	OH & 16354.682 & 0.011 & 0.003 & 4.167 \\
	OH & 16364.626 & 0.007 & 0.003 & 2.661 \\
	OH & 16368.244 & 0.008 & 0.002 & 4.303 \\
	OH & 16581.281 & 0.008 & 0.002 & 4.41 \\
	OH & 16581.74 & 0.004 & 0.001 & 4.842 \\
	OH & 16866.621 & 0.005 & 0.001 & 3.169 \\
	OH & 16871.982 & 0.012 & 0.002 & 4.892 \\
	OH & 16878.976 & 0.006 & 0.002 & 3.807 \\
	OH & 16884.573 & 0.005 & 0.002 & 3.066 \\
	OH & 16886.206 & 0.006 & 0.001 & 5.131 \\
	OH & 16895.074 & 0.005 & 0.002 & 2.197 \\
	Fe I & 15207.509 & -0.007 & 0.003 & -2.622 \\
	Fe I & 15648.478 & -0.006 & 0.002 & -3.273 \\
	Fe I & 15692.643 & -0.008 & 0.002 & -4.056 \\
	Si I & 15960.044 & -0.009 & 0.004 & -2.523 \\
	Si I & 16094.893 & -0.014 & 0.003 & -4.368 \\
	Si I & 16680.77 & -0.01 & 0.003 & -3.475 \\
	K I & 15162.824 & -0.006 & 0.002 & -2.294 \\
	Ti I & 15715.641 & 0.006 & 0.002 & 2.894 \\
	Ti I & 16634.973 & 0.003 & 0.001 & 4.224 \\
	V I & 15923.924 & 0.003 & 0.001 & 3.6 \\
	Mn I & 15159.054 & -0.006 & 0.002 & -3.123 \\
	\enddata
\end{deluxetable}
